\LARGE \bf Reactive Trajectory Planning and Trajectory Tracking for Pedestrian-Aware Autonomous Driving in Urban Environments

### 2016-01-23 root.tex
update to section IV-A... oops

The problem is defined by the vector of known values $\mathbf{b}  = [v_i, a_i, L, v_m, v_f]$, being initial speed, initial acceleration, the total distance, speed limit, and the final speed, respectively.
Final forward acceleration is set to zero.
If $\mathbf{a}_m = [a^+_m , a^-_m]$ and $\mathbf{j}_m = [j^+_m , j^-_m]$. are known, then a profile with $M$ jerk phases (7 in this case) can be generated by solving for the time intervals $[\Delta t_1, ..., \Delta t_M]$.
Jerk and peak acceleration may be different when reducing speed versus increasing speed to more closely mirror human driving behavior.
As we show later, peak acceleration and jerk must sometimes be modified to obtain physically possible time intervals.
To enable this, ranges of acceptable longitudinal jerk and acceleration $\mathbf{a}^{max}_m = [a^{+,max}_m , a^{-,max}_m]$ and $\mathbf{j}^{max}_m = [j^{+,max}_m , j^{-,max}_m]$ are set according to the relation in Eqs. \ref{eq:am} and \ref{eq:jm}.
This is computed for every point along the subpath.
In the simplest case, one value for each of the quantities expressed in these relations may be chosen for the entire path.

>>>>

Final forward acceleration is set to zero.
A profile with $M$ jerk phases (7 in this case) can be generated by solving for the time intervals $[\Delta t_1, ..., \Delta t_M]$.
As we show later, $\mathbf{a}_m$, and $\mathbf{j}_m$ must sometimes be modified to obtain physically possible time intervals.
To enable this, ranges of acceptable longitudinal jerk and acceleration $\mathbf{a}^{max}_m = [a^{+,max}_m , a^{-,max}_m]$ and $\mathbf{j}^{max}_m = [j^{+,max}_m , j^{-,max}_m]$ are set according to the relation in Eqs. \ref{eq:am} and \ref{eq:jm}.
In the simplest case, one value for each of the quantities expressed in these relations may be chosen for the entire path.
